---
title: "Urbanicity Scale"
author: "Shozen Dan, Nicholas Ortega"
date: "8/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(multilevel)
library(ltm)
library(psych)
library(tidyverse)
library(haven)
```

```{r import datasets, message=FALSE, warning=FALSE}
# Community data and PSU
community<- read_dta("../../data/Community_2011.dta")
psu <- read_dta("../../data/PSU.dta")

# Scores
econ <- read_csv("../../Scores/Community/economic.csv")
social <- read_csv("../../Scores/Community/social.csv")
pop <- read_csv("../../Scores/Community/population.csv")
house <- read_csv("../../Scores/Community/housing.csv")
trans <- read_csv("../../Scores/Community/transportation.csv")  
edu <- read_csv("../../Scores/Community/education.csv")
market <- read_csv("../../Scores/Community/market.csv")
div <- read_csv("../../Scores/Community/diversity.csv")
```

```{r message=FALSE}
# Join datasets
urban.score <- econ %>% 
  left_join(social) %>%
  left_join(pop) %>%
  left_join(house) %>%
  left_join(trans) %>%
  left_join(edu) %>% 
  left_join(market) %>% 
  left_join(div)

items <- urban.score %>% 
  select(
    urban_score_pop, 
    urban_score_edu,
    urban_score_markets,
    urban_score_trans,
    urban_score_housing,
    urban_score_econ,
    urban_score_div, # Remove diversity
    urban_score_soc
  ) 
```

## Exploratory Factor Analysis
```{r}
# Factor analysis
items.fa <- factanal(items, factors = 1)
items.fa
```
Diversity, education, and social services show an extremely high value of uniqueness. Therefore we will remove them from our scale.

```{r}
items2 <- urban.score %>% 
  select(
    urban_score_pop, 
    urban_score_markets,
    urban_score_trans,
    urban_score_housing,
    urban_score_econ,
    urban_score_div
  ) 
```

```{r}
# Factor analysis
items2.fa <- factanal(items2, factors = 1)
items2.fa
```

## Cronbach's Alpha
```{r}
ltm::cronbach.alpha(items2, na.rm=TRUE)
```

## Item-Scale Correlation
```{r}
itemscale.res <- multilevel::item.total(items2)
itemscale.res
```

## Reciever Operator Characteristics
```{r}
library(plotROC)
items2$communityID <- urban.score$communityID
items2 <- items2 %>% 
  left_join(select(psu, communityID, urban_nbs), by="communityID") %>%
  mutate(urban_score = urban_score_econ + urban_score_pop + urban_score_housing + urban_score_trans + urban_score_markets + urban_score_div)
```

```{r fig.width = 6, fig.height = 6}
ggplot(items2, aes(d = urban_nbs, m = urban_score)) + 
  geom_roc() + 
  style_roc()
```
```{r}
threshold <- 31.3

urban_flag <- items2 %>% 
  mutate(
    urban_flag = ifelse(urban_score >= threshold, 1, 0)
  ) %>% 
  pull(urban_flag)

urban_nbs <- as.numeric(psu$urban_nbs)
```

```{r}
item2.kappa <- psych::cohen.kappa(cbind(urban_flag, urban_nbs))
item2.kappa$kappa
```
The Kappa Coefficient is 0.665 indicating substantial agreement between scale and urban_nbs (Interpretation of Kappa tend to be arbitrary)

### Export Final Internally Validated Scale
```{r}
items2 %>% 
  select(-urban_nbs) %>% 
  write_csv("../../Scores/Community/urbanicity.csv")
```




