---
title: "Construct Validity: Health Care Scheme"
author: "Shozen Dan"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
```

```{r message=FALSE}
urb.scores <- read_csv('../../Scores/Individual/urbanicity_weighted.csv')
health.2011 <- read_dta('../../data/Healthcare_and_Insurance_2011.dta')
health.2013 <- read_dta('../../data/Healthcare_and_Insurance_2013.dta')
health.2015 <- read_dta('../../data/Healthcare_and_Insurance_2015.dta')
health.2018 <- read_dta('../../data/Healthcare_and_Insurance_2018.dta')
```

### 2011 Survey
`ea001s1`: Urban Employee Medical Insurance
`ea001s2`: Urban Resident Medical Insurance
`ea001s3`: New Cooperative Medical Insurance
`ea001s4`: Urban and Rural Residence Medial Insurance

### 2015 Survey
`ea003_1_`: Where set up: Urban Employee Medical Insurance
`ea003_2_`: Where set up: Urban Resident Medical Insurance
`ea003_3_`: Where set up: New Cooperative Medical Insurance
`ea003_4_`: Where set up: Urban and Rural Residence Medial Insurance

### 2018 Survey
`ea001_w4_s1`: Urban Employee Medical Insurance
`ea001_w4_s2`: Urban and Rural Residence Medial Insurance
`ea001_w4_s3`: Urban Resident Medical Insurance
`ea001_w4_s4`: New Cooperative Medical Insurance

```{r}
health.2011 <- health.2011 %>% 
  select(communityID, ea001s1, ea001s2, ea001s3, ea001s4) %>% 
  mutate(
    ea001s1 = ifelse(!is.na(ea001s1), 1, 0),
    ea001s2 = ifelse(!is.na(ea001s2), 1, 0),
    ea001s3 = ifelse(!is.na(ea001s3), 1, 0),
    ea001s4 = ifelse(!is.na(ea001s4), 1, 0)
  )

health.2013 <- health.2013 %>% 
  select(communityID, ea001s1, ea001s2, ea001s3, ea001s4) %>% 
  mutate(
    ea001s1 = ifelse(!is.na(ea001s1), 1, 0),
    ea001s2 = ifelse(!is.na(ea001s2), 1, 0),
    ea001s3 = ifelse(!is.na(ea001s3), 1, 0),
    ea001s4 = ifelse(!is.na(ea001s4), 1, 0)
  )

health.2015 <- health.2015 %>% 
  select(communityID, ea003_1_, ea003_2_, ea003_3_, ea003_4_) %>% 
  mutate(
    ea003_1_ = ifelse(!is.na(ea003_1_), 1, 0),
    ea003_2_ = ifelse(!is.na(ea003_2_), 1, 0),
    ea003_3_ = ifelse(!is.na(ea003_3_), 1, 0),
    ea003_4_ = ifelse(!is.na(ea003_4_), 1, 0)
  )

health.2018 <- health.2018 %>% 
  select(communityID, ea001_w4_s1, ea001_w4_s2, ea001_w4_s3, ea001_w4_s4) %>% 
  mutate(
    ea001_w4_s1 = ifelse(ea001_w4_s1 == 1, 1, 0),
    ea001_w4_s2 = ifelse(ea001_w4_s2 == 2, 1, 0),
    ea001_w4_s3 = ifelse(ea001_w4_s3 == 3, 1, 0),
    ea001_w4_s4 = ifelse(ea001_w4_s4 == 4, 1, 0)
  )
```

```{r}
urb.2011 <- urb.scores %>% filter(year == 2011)
urb.quint.2011 <- quantile(urb.2011$urban_score, prob=seq(0,1,0.2))
urb.2011 <- urb.2011 %>% 
  mutate(
    quintile = case_when(
      urban_score < urb.quint.2011[2] ~ "Q1",
      urban_score < urb.quint.2011[3] ~ "Q2",
      urban_score < urb.quint.2011[4] ~ "Q3",
      urban_score < urb.quint.2011[5] ~ "Q4",
      urban_score <= urb.quint.2011[6] ~ "Q5"
    )
  )

urb.2013 <- urb.scores %>% filter(year == 2013)
urb.quint.2013 <- quantile(urb.2013$urban_score, prob=seq(0,1,0.2))
urb.2013 <- urb.2013 %>% 
  mutate(
    quintile = case_when(
      urban_score < urb.quint.2013[2] ~ "Q1",
      urban_score < urb.quint.2013[3] ~ "Q2",
      urban_score < urb.quint.2013[4] ~ "Q3",
      urban_score < urb.quint.2013[5] ~ "Q4",
      urban_score <= urb.quint.2013[6] ~ "Q5"
    )
  )

urb.2015 <- urb.scores %>% filter(year == 2015)
urb.quint.2015 <- quantile(urb.2015$urban_score, prob=seq(0,1,0.2))
urb.2015 <- urb.2015 %>% 
  mutate(
    quintile = case_when(
      urban_score < urb.quint.2015[2] ~ "Q1",
      urban_score < urb.quint.2015[3] ~ "Q2",
      urban_score < urb.quint.2015[4] ~ "Q3",
      urban_score < urb.quint.2015[5] ~ "Q4",
      urban_score <= urb.quint.2015[6] ~ "Q5"
    )
  )

urb.2018 <- urb.scores %>% filter(year == 2018)
urb.quint.2018 <- quantile(urb.2018$urban_score, prob=seq(0,1,0.2))
urb.2018 <- urb.2018 %>% 
  mutate(
    quintile = case_when(
      urban_score < urb.quint.2018[2] ~ "Q1",
      urban_score < urb.quint.2018[3] ~ "Q2",
      urban_score < urb.quint.2018[4] ~ "Q3",
      urban_score < urb.quint.2018[5] ~ "Q4",
      urban_score <= urb.quint.2018[6] ~ "Q5"
    )
  )

health.2011 <- health.2011 %>% 
  left_join(urb.2011, by="communityID") %>% 
  mutate(
    urb_ins = ifelse(ea001s1 == 1 | ea001s2 == 1,1,0), # UBEMI & UBRMI
    rur_ins = ifelse(ea001s3 == 1,1,0) # NCMI
  )

health.2013 <- health.2013 %>% 
  left_join(urb.2013, by="communityID") %>% 
  mutate(
    urb_ins = ifelse(ea001s1 == 1 | ea001s2 == 1,1,0), # UBEMI & UBRMI
    rur_ins = ifelse(ea001s3 == 1,1,0) # NCMI
  )

health.2015 <- health.2015 %>% 
  left_join(urb.2015, by="communityID") %>% 
  mutate(
    urb_ins = ifelse(ea003_1_ == 1 | ea003_2_ == 1,1,0), # UBEMI & UBRMI
    rur_ins = ifelse(ea003_3_ == 1,1,0) # NCMI
  )

health.2018 <- health.2018 %>% 
  left_join(urb.2018, by="communityID") %>% 
  mutate(
    urb_ins = ifelse(ea001_w4_s1 == 1 | ea001_w4_s3 == 1,1,0), # UBEMI & UBRMI
    rur_ins = ifelse(ea001_w4_s4 == 1,1,0) # NCMI
  )
```

## Urban Medical Insurance
```{r}
logit.urb_ins.2011 <- glm(urb_ins ~ quintile, health.2011, family = "binomial")
logit.urb_ins.2013 <- glm(urb_ins ~ quintile, health.2013, family = "binomial")
logit.urb_ins.2015 <- glm(urb_ins ~ quintile, health.2015, family = "binomial")
logit.urb_ins.2018 <- glm(urb_ins ~ quintile, health.2018, family = "binomial")

summary(logit.urb_ins.2011)
summary(logit.urb_ins.2013)
summary(logit.urb_ins.2015)
summary(logit.urb_ins.2018)
```

```{r}
health.2011$year <- 2011
health.2013$year <- 2013
health.2015$year <- 2015
health.2018$year <- 2018

df.healthins <- rbind(
  select(health.2011, communityID, year, urban_score, quintile, urb_ins, rur_ins),
  select(health.2013, communityID, year, urban_score, quintile, urb_ins, rur_ins),
  select(health.2015, communityID, year, urban_score, quintile, urb_ins, rur_ins),
  select(health.2018, communityID, year, urban_score, quintile, urb_ins, rur_ins)
)

df.healthins <- df.healthins %>% 
  group_by(quintile, year) %>% 
  summarise(
    urban_score = mean(urban_score,na.rm=T),
    urb_ins = mean(urb_ins, na.rm=T),
    rur_ins = mean(rur_ins, na.rm=T)
  ) %>% 
  drop_na() %>% 
  pivot_longer(cols = ends_with("ins"), names_to = "type", values_to = "rate")

ggplot(df.healthins, aes(x=urban_score, y=rate, color=type, shape=factor(year))) + 
  geom_point(size=2.3, alpha=0.8) + 
  geom_line(alpha=0.6) + 
  scale_x_continuous(breaks = seq(0,40,5), limits=c(5,38)) + 
  scale_y_continuous(breaks = seq(0,1,0.2), limits=c(0,1), labels = scales::percent_format(accuracy = 5L)) + 
  scale_color_manual(labels = c("Rural", "Urban"), values = c("#003f5c", "#ffa600")) + 
  labs(
    x = "Urbanicity Score", 
    y="Enrollement Rate",
    shape="Year",
    color="Type"
  ) + 
  theme_minimal() + 
  theme(legend.position = "bottom")
```


## New Cooperative Medical Insurance
```{r}
ncmi.2011 <- glm(ea001s3 ~ quintile, health.2011, family = "binomial")
ncmi.2013 <- glm(ea001s3 ~ quintile, health.2013, family = "binomial")
ncmi.2015 <- glm(ea003_3_ ~ quintile, health.2015, family = "binomial")
ncmi.2018 <- glm(ea001_w4_s4 ~ quintile, health.2018, family = "binomial")

summary(ncmi.2011)
summary(ncmi.2013)
summary(ncmi.2015)
summary(ncmi.2018)

exp(ncmi.2018$coefficients)
```

## Urban and Rural Residence Medial Insurance
```{r}
urrmi.2011 <- glm(ea001s4 ~ quintile, health.2011, family = "binomial")
urrmi.2013 <- glm(ea001s4 ~ quintile, health.2013, family = "binomial")
urrmi.2015 <- glm(ea003_1_ ~ quintile, health.2015, family = "binomial")
urrmi.2018 <- glm(ea001_w4_s2 ~ quintile, health.2018, family = "binomial")

summary(urrmi.2011)
summary(urrmi.2013)
summary(urrmi.2015)
summary(urrmi.2018)
```

